\textbf{Proof Reconstruction in Classical Propositional Logic}

### 2017-06-17 slides/Jonathan-Proof-Reconstruction.tex
[ slides ] updated info added and fixed phi symbols.

\title[Proof Reconstruction in Classical Propositional Logic]
  {\textbf{Proof Reconstruction in Classical Propositional Logic}}
\subtitle{(work in progress)}
\date{May 11, 2017
}
\author[Jonathan Prieto-Cubides]{Jonathan Prieto-Cubides\\
(joint work with Andr\'es Sicard-Ram\'irez)}
\institute{
Master in Applied Mathematics\\
Universidad EAFIT\\
Medell\'in, Colombia}
% --------------------------------------------------------------------------

@@

\vfill
\begin{itemize}
\item Definition
\begin{equation*}
\text{\color{plum!40!black}conjunct}(\overbrace{ϕ₁ ∧ ⋯ ∧ \phi_n}^{\phi}, \psi)
= \begin{cases}
\phi_{i} \ \ \ \ \text{if }\psi\text{ is equal to some }\phi_i\\
\phi    \ \ \ \ \text{otherwise}
\end{cases}
\end{equation*}

@@

 \begin{prooftree}
  \AxiomC{$ϕ₁ ∧ φ₂$}
  \RightLabel{\scriptsize $∧$-\texttt{proj}$₁$}
  \UnaryInfC{$ϕ₁$}
  \end{prooftree}
\end{column}

\begin{column}{0.42\textwidth}
 \begin{prooftree}
  \AxiomC{$ϕ₁ ∧ φ₂$}
  \RightLabel{\scriptsize $∧$-\texttt{proj}$₂$}
  \UnaryInfC{$φ₂$}
  \end{prooftree}
\end{column}

\begin{column}{0.2\textwidth}  %%<--- here
  \begin{tikzpicture}[
    ->
  , >=stealth'
  , shorten >=1pt
  , auto
%  , node distance=2.8cm
  , thick
  , every state/.style={fill=plum!45!black,draw=none,text=white}
  , overlay
  , remember picture
    , transform canvas={scale=.75}
    ]
  \tikzset{shift={(current page.center)}, xshift=4.5cm,yshift=1cm}

  \node[state]  (phi)                     {$φ$};
  \node[state]  (phi1) [below left =1.3cm and 0.1cm of phi]  {$φ₁$};
  \node[state]  (phi2) [below right=1.3cm and 0.1cm of phi]  {$φ₂$};
  \node[state]  (phi3)  [below left =1.3cm and 0.1cm of phi2]  {$φ₃$};
  \node[state]  (phi4)  [below right =1.3cm and 0.1cm of phi2]  {$φ₄$};

@@

\item Example
\[ φ := φ₁ ∧ \overbrace{(φ₃ ∧ φ₄)}^{φ₂}\]

@@

\item
\texttt{conjunct}$(φ , φ₃ ∧ φ₁) ≡ ϕ$
\vskip 3mm
\item
\texttt{conjunct}$(φ , φ₃)      ≡ ϕ₃$
\vskip 3mm
\item
\texttt{conjunct}$(φ , φ₂)      ≡ ϕ₂$
\vskip 3mm
\end{itemize}

@@

\begin{frame}[fragile, label=atp-conjunct-proof]{The \texttt{conjunct} function and its theorem, \texttt{atp-conjunct}}
\vfill
\begin{minted}{cagda}
conjunct : (φ ψ : Prop) → Prop
conjunct φ ψ with conj-view φ | conjunct-path φ ψ []
... | _          | []           = φ
... | conj _ _ | pick  ∷ path = φ
... | conj φ₁ _ | proj₁ ∷ path = conjunct φ₁ ψ
... | conj _ φ₂ | proj₂ ∷ path = conjunct φ₂ ψ
... | other .φ   | _            = φ

atp-conjunct
  : ∀ {Γ} {φ}
  → Γ ⊢ φ
  → (ψ : Prop)
  → Γ ⊢ conjunct φ ψ

atp-conjunct {Γ} {φ} Γ⊢φ ψ
  with conj-view φ | conjunct-path φ ψ []
...  | _          | []           = Γ⊢φ
...  | conj φ₁ φ₂ | pick  ∷ path = Γ⊢φ
...  | conj φ₁ φ₂ | proj₁ ∷ path = atp-conjunct ψ (∧-proj₁ Γ⊢φ)
...  | conj φ₁ φ₂ | proj₂ ∷ path = atp-conjunct ψ (∧-proj₂ Γ⊢φ)
...  | other .φ   | (_ ∷ _)      = Γ⊢φ
\end{minted}
\vfill
\gobackreconstruction
\end{frame}

@@

-- Axiom.
a = (p ∧ q)

@@

-- Conjecture.
goal = (q ∧ p)

-- Subgoals.
subgoal₀ = q
subgoal₁ = (q ⇒ p)
\end{minted}
\vfill
\end{frame}

\begin{frame}[fragile, label=verified-example-2]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
\vfill
\begin{minted}{cagda}
a : Prop
a = (p ∧ q)

@@

\begin{frame}[fragile, label=verified-example-3]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
\vfill
\begin{minted}{cagda}
subgoal₁ : Prop
subgoal₁ = (q ⇒ p)

@@

-- Conjecture.
goal = (q ∧ p)

-- Subgoals.
subgoal₀ = q
subgoal₁ = (q ⇒ p)

>>>>

\title[Proof Reconstruction in Classical Propositional Logic]
  {\textbf{Proof Reconstruction in Classical Propositional Logic}}
\subtitle{(work in progress)}
\date{May 11, 2017\\Updated: \today}
\author[Jonathan Prieto-Cubides]{Jonathan Prieto-Cubides\\
(joint work with Andr\'es Sicard-Ram\'irez)}
\institute{
Master in Applied Mathematics\\
Universidad EAFIT\\
Medell\'in, Colombia}
% --------------------------------------------------------------------------

@@

\vfill
\begin{itemize}
\item Definition
\begin{equation*}
\text{\color{plum!40!black}conjunct}(\overbrace{\varphi_1 ∧ ⋯ ∧ \varphi_n}^{\varphi}, \psi)
= \begin{cases}
\varphi_{i} \ \ \ \ \text{if }\psi\text{ is equal to some }\varphi_i\\
\varphi    \ \ \ \ \text{otherwise}
\end{cases}
\end{equation*}

@@

 \begin{prooftree}
  \AxiomC{$\varphi_1 ∧ \varphi_2$}
  \RightLabel{\scriptsize $∧$-\texttt{proj}$₁$}
  \UnaryInfC{$\varphi_1$}
  \end{prooftree}
\end{column}

\begin{column}{0.42\textwidth}
 \begin{prooftree}
  \AxiomC{$\varphi_1 ∧ \varphi_2$}
  \RightLabel{\scriptsize $∧$-\texttt{proj}$₂$}
  \UnaryInfC{$\varphi₂$}
  \end{prooftree}
\end{column}

\begin{column}{0.2\textwidth}  %%<--- here
  \begin{tikzpicture}[
    ->
  , >=stealth'
  , shorten >=1pt
  , auto
%  , node distance=2.8cm
  , thick
  , every state/.style={fill=plum!45!black,draw=none,text=white}
  , overlay
  , remember picture
    , transform canvas={scale=.75}
    ]
  \tikzset{shift={(current page.center)}, xshift=4.5cm,yshift=0cm}

  \node[state]  (phi)                     {$\varphi$};
  \node[state]  (phi1) [below left =1.3cm and 0.1cm of phi]  {$\varphi_1$};
  \node[state]  (phi2) [below right=1.3cm and 0.1cm of phi]  {$\varphi_2$};
  \node[state]  (phi3)  [below left =1.3cm and 0.1cm of phi2]  {$\varphi_3$};
  \node[state]  (phi4)  [below right =1.3cm and 0.1cm of phi2]  {$\varphi_4$};

@@

\item Example
\[ \varphi := \varphi_1 ∧ \overbrace{(\varphi_3 ∧ \varphi_4)}^{\varphi_2}\]

@@

\item
\texttt{conjunct}$(\varphi , \varphi_3 ∧ \varphi_1) ≡ \varphi$
\vskip 3mm
\item
\texttt{conjunct}$(\varphi , \varphi_3)      ≡ \varphi_3$
\vskip 3mm
\item
\texttt{conjunct}$(\varphi , \varphi_2)      ≡ \varphi_2$
\vskip 3mm
\end{itemize}

@@

\begin{frame}[fragile, label=atp-conjunct-proof]{The \texttt{conjunct} function and its theorem, \texttt{atp-conjunct}}
\vfill
\begin{minted}{cagda}
conjunct : (φ ψ : Prop) → Prop
conjunct φ ψ with conj-view φ | conjunct-path φ ψ []
... | _          | []        = φ
... | conj _ _   | pick  ∷ _ = φ
... | conj φ₁ _  | proj₁ ∷ _ = conjunct φ₁ ψ
... | conj _ φ₂  | proj₂ ∷ _ = conjunct φ₂ ψ
... | other .φ   | _         = φ

atp-conjunct
  : ∀ {Γ} {φ}
  → (ψ : Prop)
  → Γ ⊢ φ
  → Γ ⊢ conjunct φ ψ

atp-conjunct {Γ} {φ} ψ Γ⊢φ
  with conj-view φ | conjunct-path φ ψ []
...  | _           | []        = Γ⊢φ
...  | conj _ _    | pick  ∷ _ = Γ⊢φ
...  | conj _ _    | proj₁ ∷ _ = atp-conjunct ψ (∧-proj₁ Γ⊢φ)
...  | conj _ _    | proj₂ ∷ _ = atp-conjunct ψ (∧-proj₂ Γ⊢φ)
...  | other _     | (_ ∷ _)   = Γ⊢φ
\end{minted}
\vfill
\gobackreconstruction
\end{frame}

@@

-- Axiom.
a = p ∧ q

@@

-- Conjecture.
goal = q ∧ p

-- Subgoals.
subgoal₀ = q
subgoal₁ = q ⇒ p
\end{minted}
\vfill
\end{frame}

\begin{frame}[fragile, label=verified-example-2]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
\vfill
\begin{minted}{cagda}
a : Prop
a = p ∧ q

@@

\begin{frame}[fragile, label=verified-example-3]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
\vfill
\begin{minted}{cagda}
subgoal₁ : Prop
subgoal₁ = q ⇒ p

@@

-- Conjecture.
goal = q ∧ p

-- Subgoals.
subgoal₀ = q
subgoal₁ = q ⇒ p
